Community Similarity Analysis

### 2022-10-03 scripts/workshop/comm_similarity.Rmd
update scripts with date
update distances

---
title: "Community Similarity Analysis"
author: "Daniel Suh"
date: "2022-10-03"
output: html_document
---

@@

Manhattan method is the absolute value of the difference between two values
So higher distance means larger difference
Normalized distances to have range 0 to 1
```{r}
cc_diff <- comm_summ %>% dplyr::select(siteID, cc) %>% mutate(log_cc = log1p(cc)) %>% dplyr::select(-cc)
cc_dist <- dist(cc_diff, method = "manhattan")
cc_diff_mat <- as.matrix(cc_dist, labels = T)
colnames(cc_diff_mat) <- cc_diff[[1]]
rownames(cc_diff_mat) <- cc_diff[[1]]
cc_diff_df <- melt(cc_diff_mat, varnames=c("row", "col"), value.name = "cc_dist") %>% 
  mutate(cc_norm = (cc_dist-min(.$cc_dist))/(max(.$cc_dist)-min(.$cc_dist)))

@@

```{r}
j_dist <- dist(delta_j, method = "manhattan")
j_dist_mat <- as.matrix(j_dist, labels = T)
colnames(j_dist_mat) <- delta_j[[1]]
rownames(j_dist_mat) <- delta_j[[1]]

@@

```{r}
p_dist <- dist(delta_p, method = "manhattan")
p_dist_mat <- as.matrix(p_dist, labels = T)
colnames(p_dist_mat) <- delta_p[[1]]
rownames(p_dist_mat) <- delta_p[[1]]

>>>>

---
title: "Community Similarity Analysis"
author: "Daniel Suh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

Manhattan method is the absolute value of the difference between two values
So higher distance means larger difference
Normalized distances to have range 0 to 1
```{r}
cc_diff <- comm_summ %>% dplyr::select(siteID, cc) %>% mutate(log_cc = log1p(cc)) %>% dplyr::select(-cc)
cc_dist <- dist(cc_diff$log_cc, method = "manhattan")
cc_diff_mat <- as.matrix(cc_dist, labels = T)
colnames(cc_diff_mat) <- cc_diff[[1]]
rownames(cc_diff_mat) <- cc_diff[[1]]
cc_diff_df <- melt(cc_diff_mat, varnames=c("row", "col"), value.name = "cc_dist") %>% 
  mutate(cc_norm = (cc_dist-min(.$cc_dist))/(max(.$cc_dist)-min(.$cc_dist)))

@@

```{r}
j_dist <- dist(delta_j$J, method = "manhattan")
j_dist_mat <- as.matrix(j_dist, labels = T)
colnames(j_dist_mat) <- delta_j[[1]]
rownames(j_dist_mat) <- delta_j[[1]]

@@

```{r}
p_dist <- dist(delta_p$P, method = "manhattan")
p_dist_mat <- as.matrix(p_dist, labels = T)
colnames(p_dist_mat) <- delta_p[[1]]
rownames(p_dist_mat) <- delta_p[[1]]
